Methods with preconditioning with weight decay regularization

### 2023-03-29 paper/main.tex
change abstract and add cites for methods

\section{Introduction}
In machine learning we consider unconstrained optimization problem
\begin{equation*}
	\min_{w \in \mathbb{R}^d} f(w)
\end{equation*}
Problems of the form (1) cover a plethora of applications, including empirical risk minimization,
deep learning, and supervised learning tasks such as regularized least squares or logistic regression. This minimization problem can be difficult to solve, particularly when the number of training
samples n, or problem dimension d, is large, or if the problem is nonconvex.

There are second order preconditioners methods for solving this problem, such as Adam \citep{kingma2014adam} , OASIS \citep{}, AdaHessian.

@@

\section{Problem statement}
We consider the unconstrained optimization problem
\begin{equation*}
	\min_{w \in \mathbb{R}^d} f(w)
\end{equation*}
Problems of the form cover a plethora of applications, including empirical risk minimization,
deep learning, and supervised learning tasks such as regularized least squares or logistic regression.

>>>>

\section{Introduction}
In machine learning we consider unconstrained optimization problem
\begin{equation}
	\min_{w \in \mathbb{R}^d} f(w)
\end{equation}
Problems of the form (1) cover a plethora of applications, including empirical risk minimization,
deep learning \citep{lecun2015deep}, and supervised learning \citep{cunningham2008supervised} tasks such as regularized least squares \citep{rifkin2007notes} or logistic regression \citep{shalev2014understanding}. This minimization problem can be difficult to solve, particularly when the number of training
samples n, or problem dimension d, is large, or if the problem is nonconvex.

Second order preconditioners methods are methods when instead of calculate true hessian of our function for newton method \citep{dennis1977quasi}, some heuristics is used to calculate pseudo-hessian. There are second order preconditioners methods for solving this problem, such as Adam \citep{kingma2014adam} , OASIS \citep{goldberg2011oasis}, AdaHessian \citep{yao2021adahessian}.

@@

\section{Problem statement}

We consider the unconstrained optimization problem
\begin{equation*}
	\min_{w \in \mathbb{R}^d} f(w)
\end{equation*}
Problems of the form cover a plethora of applications, including empirical risk minimization,
deep learning, and supervised learning tasks such as regularized least squares or logistic regression.
